### 2024-07-13 basic-statistics.qmd
20240913 - additions and clean up

>>>>

To draw statistical inferences, the frequentist statistics paradigm leverages null hypothesis significance testing.
Frequentist statistics is the most widely used statistical paradigm.
However, frequentist statistics is not the only statistical paradigm.
Other statistical paradigms exist, including [Bayesian statistics](#sec-bayesTheorem), which is based on [Bayes' theorem](#sec-bayesTheorem).
This chapter focuses on the frequentist approach to hypothesis testing, known as null hypothesis significance testing.
We discuss Bayesian statistics in @sec-baseRates.
